---
title: "Miscellaneous Tensorflow Operations"
author: "Will Townes"
date: "2/16/2018"
output: html_document
---

```{r}
library(tensorflow)
```

broadcasting- tensorflow equivalent of R's vector recycling

```{r}
#z32<-tf$constant(matrix(0,nrow=3,ncol=2),dtype="float32")
z<-tf$constant(diag(3),dtype="float32")
a<-tf$constant(c(1,-2,3))
a2<-tf$constant(matrix(c(1,-2,3)),dtype="float32")
sess<-tf$Session()
sess$run(z+a)
sess$run(a+z)
sess$run(tf$transpose(a)+z)
sess$run(tf$transpose(tf$transpose(z)+a))
sess$run(z+a2)
sess$close()
```

conclusion about broadcasting:

* tensorflow supports recycling but the default mode is to recycle across the last dimension first, which is the opposite of R which recycles across the first dimension.
* there are two ways to force recycling across rows instead. The first is to change the representation of the vector into a 3x1 matrix instead of a 3-vector. The matrix representation then aligns along the rows of the z. Alternatively, one can transpose the larger array and then transpose again after the recycling operation
